### 2024-09-24 sections/awards.tex
Update awards.tex

\begin{cvhonors}
\cvhonor
{ECPR Joint Sessions of Workshops Grant}
{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, {\pounds} 1 350.}
{Toulouse, FRA}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, {\pounds} 1 400.}
{Bath, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, {\pounds} 2 255.} 
{Oxford, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), {\pounds} 160 000.}
{Oxford, GBR}
{2019}
\end{cvhonors}

@@

%% \begin{cvhonors}
%% \cvhonor
%% {LASA Travel Grant} 
%% {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400}
%% {New York, USA}
%% {2016}
%% \end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), {\pounds} 1 150.}
{Santiago, CHL}
{2012}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{Early Career Scholar Award}
{Best early career work and travel support for the BigSurv23 Conference, about {\pounds} 525.}
{Quito, ECU}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ECPR Joint Sessions of Workshops Grant}
{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, about {\pounds} 1 350.}
{Toulouse, FRA}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, about {\pounds} 1 400.}
{Bath, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, about {\pounds} 2 255.} 
{Oxford, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), about {\pounds} 160 000.}
{Oxford, GBR}
{2019}
\end{cvhonors}

%% \begin{cvhonors}
%% \cvhonor
%% {LASA Travel Grant} 
%% {Travel support for the XXXIV International Congress of the Latin American Studies Association (LASA/40071), {\pounds} 400.}
%% {New York, USA}
%% {2016}
%% \end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), about {\pounds} 1 150.}
{Santiago, CHL}
{2012}
\end{cvhonors}
